S19: REU Research Document

### 2019-06-24 paper.tex
Add files via upload

\title{S19: REU Research Document}
\author{Emily Slaughter, Gennie Mansi }

@@

Proper documentation forms an integral part of developing and maintaining software, especially given the increasing size of code bases and the prevalence of temporally and spatially dispersed teams. As code is written and the project develops, various design decisions are made, which impact both existing and future code. Documentation of design decisions and the rational behind those decisions is dependent on the developer and is often recorded or dispersed between several disparate locations, including a formal document, comments in the code, and the developers themselves. However, documentation is often not written, read, or updated, causing developers to depend largely on the code and other sources of information rather than explicit, written documentation.

Ideally, as code is authored or modified, it should follow previous design rules use to author prior code.
The \textit{design rules} for a project is the set of choices about the code's design and how those choices were implemented. Several sources of information, including search history, cursor location, event logs, debugger information, and the code itself can indicate what elements in the code base are most pertinent to the user and are most likely to contain design rules of interest. Some information about design rules may only be recorded in the memories of co-workers, and thus access to this kind of information is also critical for developers trying to understand and use an existing code base.

Mixed human-AI authoring of code patterns can greatly assist developers to efficiently and accurately develop and maintain a unified set of rules. There are an infinite number of patterns that could be found in a given code base; therefore, the crux of the problem lies in determining which patterns in the given code should be used to train the machine learning algorithm. Hence our focus is on mining design rules from a given code base in any language in order to facilitate active documentation and maintenance of code.

We explore how information from outside of the code base could be used to inform what patterns are identified.We seek to develop a tool that combines that has both automatic and manual rule-authoring capabilities. It should also automatically provide live updates with examples and violations of authored design rules. Ultimately, such a tool will greatly increase the amount of up-to-date documentation available to developers.

@@

Developers can be divided into three categories with respect to their familiarity with a project or code base. First, a developer may be experienced with a given code base. She would have a thorough understanding of the project, its objectives, and its implementation. She is in a position that allows her to author design rules and verify that certain rules have been followed through the project. Second, a developer may be partially knowledgable about a project and its implementation. Such a developer may have a general familiarity with the code and its implementations, but is not able to easily or confidently author design rules or may simply wish to explore possible existing design rules. On her own she is not be able to produce an accurate rule, but might be able to see a rule and provide useful feedback on its correctness or relevancy. Finally, a developer may be completely unfamiliar with a code base. Existing design rules and documents would be extremely helpful in helping her understand the structure of the code. She may also need to frequently consult co-workers about code standards and patterns if there is a significant lack of written documentation. In such a situation, the developer may even be interested in looking for examples on what kind of existing design rules to which she should adhere.

 Work has already been completed with regards to the first category, and while much research has been done in code suggestion, completely automated design rule generation seems largely unexplored (see Section~\ref{relatedWorks}). Therefore, an algorithm developed with the second category of developers in mind forms a natural bridge between human authored design rules and completely automated rule authoring. Consequently, we assume the developers for which we are designing our algorithm have some general familiarity with the code and can identify proper design rules if supplied with a set of rules to consider. Thus, feedback form the developer about hypothesized rules is dependable, enabling mixed human-AI rule authoring.

@@

Furthermore, Fritz et al conducted a survey of nineteen professional Java programmers in order to generate a degree of interest model to reflect developers' knowledge of code \cite{FritzEtAl2007}. The researchers' model was based on the total number of interactions the programmer has with an element and the recency of that interaction. Other factors they identified that could be used to improve their model included authorship of program elements, the role of elements, and the task being performed \cite{FritzEtAl2007}.

@@

\subsubsection{Filtering information}
\subsubsection{Identifying token}
\subsubsection{Generating queries}
\subsubsection{Selecting queries to present to user}

@@

Some researchers developed a tool to help a person who is new to an open-source software project find relevant artifacts to a project in order to facilitate their ability to more quickly perform a given task. They consider all of the previously produced material, including versions of the source, the bugs, archived electronic communication, and web documents, to suggest possibly relevant sources of information to a user \cite{CubranicMurphy2003}.

LaToza et al explored finding design patterns in an HTML document in order to perform code prediction \cite{LaTozaEtAl2019}. However, their tool does not identify design rules that might explain that pattern. 
ActiveDocumentation is a plug-in for IntelliJ IDEA that can be used to author rules and to view correct examples and violations of rules in a given code base in real time \cite{MehrpurEtAl2019}. The ActiveDocumentation plug-in helps the developer author, check, and fix rules, efficiently and in real time. It automatically updates its interface with correct examples and violations of design rules written in the program \cite{MehrpurEtAl2019}. Neither of these tools integrates information from sources outside of the code base such as cursor information or search history. Mylar is a tool designed for the Eclipse IDE that tries to highlight file names and code segments that are most likely to contain relevant information for a developer's current task. The highlighting is based off a model that depends on which elements of the code have been edited and accessed most recently \cite{KerstenMurphy2005}.

@@

\clearpage
%%%%%%%%%%%%%%%%%%%

\section{Discussion}\label{disc}

>>>>

\title{S19: REU Research Document}
\author{Emily Slaughter, Gennie Mansi}

@@

Proper documentation forms an integral part of developing and maintaining software, especially given the increasing size of code bases and the prevalence of temporally and spatially dispersed teams. As code is written and the project develops, various design decisions are made, which impact both existing and future code: ideally, as code is authored or modified, it should follow design rules used to author prior code. The \textit{design rules} for a project are the set of choices about the code's design and their implementation. Documentation of design rules and the rationale behind them is dependent on the developer, and when it is recorded, it is often dispersed among several disparate locations, including a formal document, comments in the code, and the developers themselves. However, documentation is often not written, read, or updated, and coworkers are not always a reliable resource \cite{KoEtAl2007}. Lack of documentation ultimately causes newcomers to a project to depend largely on the code rather than explicit, written documentation to understand such project-specific design rules.

A tool that mines and recommends design rules has the potential to facilitate active documentation of code, allowing developers to efficiently and accurately apply and maintain a unified set of design rules. There are an exponential number of patterns that could be found in a given code base, and some rules have greater relevance than others. Finding an excessive number of non-existent rules or missing important rules would discourage developers from using the tool to document their code. Hence our focus is to intelligently determine which patterns in a codebase of any language are most meaningful as rules and how to find them reasonably quickly.

Several sources of information in addition to the code itself, including search history, cursor location, event logs, and debugger information can indicate what elements in the code base are most pertinent to the user and are most likely to contain design rules of interest. We explore how this information from outside of the code base can be combined with the code base itself to inform what patterns are identified. Ultimately, such a tool will greatly increase the amount of up-to-date documentation available to developers. We seek to develop a tool that automates the manual rule-authoring capabilities of ActiveDocumentation \cite{MehrpurEtAl2019} and preserves its live-update features.

Association rule mining? Some brief description of our algorithm?

@@

Developers can be divided into three categories with respect to their familiarity with a project or code base. First, a developer may be experienced with a given code base. She has a thorough understanding of the project, its objectives, and its implementation. She is in a position that allows her to author design rules and verify that certain rules have been followed through the project. Second, a developer may be partially knowledgable about a project and its implementation. Such a developer may have a general familiarity with the code and its implementations, but is not able to easily or confidently author design rules or may simply wish to explore possible existing design rules. On her own, she is not be able to produce an accurate rule, but might be able to see a rule and provide useful feedback on its correctness or relevancy. Finally, a developer may be completely unfamiliar with a code base. Existing design rules and documents would be extremely helpful in helping her understand the structure of the code. She may also need to frequently consult co-workers about code standards and patterns if there is a significant lack of written documentation. In such a situation, the developer may even be interested in looking for examples on what kind of existing design rules to which she should adhere.

Work has already been completed with regards to the first category of developers, and while much research has been done in code suggestion, completely automated design rule generation seems largely unexplored (see Section~\ref{relatedWorks}). Therefore, an algorithm developed with the second category of developers in mind forms a natural bridge between human-authored design rules and completely automated rule authoring. Consequently, we assume the developers for which we are designing our algorithm have some general familiarity with the code and can identify proper design rules if supplied with a set of rules to consider. Thus, feedback form the developer about hypothesized rules is dependable, enabling mixed human-AI rule authoring.

@@

Furthermore, Fritz et al conducted a survey of nineteen professional Java programmers in order to generate a degree-of-interest (DOI) model to reflect developers' knowledge of code \cite{FritzEtAl2007}. The researchers' model was based on the total number of interactions the programmer has with an element and the recency of that interaction. Other factors they identified that could be used to improve their model included authorship of program elements, the role of elements, and the task being performed \cite{FritzEtAl2007}.

@@

\subsubsection{Filtering information}
\subsubsection{Generating queries}
\subsubsection{Selecting queries to present to user}

@@

Through what is called implicit group memory, Hipikat is a client-server system that automates the mentor-like relationship that develops between developers who are new to a project and senior developers who watch over the newcomers and pass down knowledge. Hipikat learn from four types of artifacts and communications stored in a project's history: bug and feature descriptions, source file revisions, messages posted on developer forums, and other project documents. Artifacts may be queried, and the artifact database may be searched \cite{CubranicAndMurphy2003}.

LaToza et al explored finding design patterns in an HTML document in order to perform code prediction \cite{LaTozaEtAl2019}. However, their tool does not identify design rules that might explain that pattern. 
ActiveDocumentation is a plug-in for IntelliJ IDEA that can be used to author rules and to view correct examples and violations of rules in a given code base in real time \cite{MehrpurEtAl2019}. The ActiveDocumentation plug-in helps the developer author, check, and fix rules, efficiently and in real time. It automatically updates its interface with correct examples and violations of design rules written in the program \cite{MehrpurEtAl2019}. Neither of these tools, however, integrates information from sources outside of the code base such as cursor information or search history. Mylar is a tool that exists within the Eclipse IDE and encodes a programmer's activity with code into a DOI model that can then be used to highlight information in a program that may be related to the task that a developer is completing. This model focuses on individual program elements without taking into account the possible structural relationships that may exist between program elements \cite{KerstenEtAl2005}.

@@
